Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-27 paper.tex
update bench

\begin{figure}
  \centering
  \begin{subfigure}[b]{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Number of hypotheses},
        ylabel={Time in ms},
        xmin=1, xmax=32,
        ymin=4, ymax=2^16,
        %xtick={1,2,4,8,16},
        %ytick={2^3,2^5,2^7,2^9,2^11,2^13},
        xmode=log,
        ymode=log,
        log basis x=2,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=}
        ]
        \addplot[
          color=orange,
          mark=square,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 6.133137) (2, 7.651537) (4, 13.290939) (8, 91.869091) (16, 1718.359150) (32, 43017.778968) 
          };
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 7.088877) (2, 9.455166) (4, 13.889670) (8, 33.293693) (16, 153.769004) (32, 1018.813208)
          };
        \addplot[
          color=orange,
          mark=o,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 8.589029) (2, 19.014450) (4, 126.356247) (8, 1560.866835) (16, 22985.414025) (32, 373397.722281) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 11.729506) (2, 22.231345) (4, 58.294695) (8, 207.863068) (16, 888.210662) (32, 3804.700212)
          };
      \end{axis}
    \end{tikzpicture}
    \caption{Transitivity benchmark}%
    \label{fig:trans}
  \end{subfigure}%
  \begin{subfigure}[b]{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Number of rules},
        %ylabel={Time in ms},
        xmin=1, xmax=32,
        ymin=4, ymax=2^16,
        ymode=log,xmode=log,
        log basis x=2,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 8.481945) (2, 13.017566) (4, 36.759979) (8, 180.629616) (16, 1156.813791) (32, 8343.946414)
          };
          \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 10.116120) (2, 11.520718) (4, 14.605806) (8, 21.079808) (16, 34.858708) (32, 64.986725)
          };
          \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 13.743712) (2, 23.221681) (4, 58.603629) (8, 235.183885) (16, 1389.365902) (32, 9687.141454) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 19.886189) (2, 30.294954) (4, 51.187760) (8, 93.739397) (16, 178.442899) (32, 351.595918)
          };
      \end{axis}
    \end{tikzpicture}
    \caption{Independence benchmark}%
    \label{fig:indep}
  \end{subfigure}
  \caption{Results of the transitivity (\subref{fig:trans}) and independence (\subref{fig:indep}) benchmarks for $a = 0$ (\protect\showpgfsquare) and $a = 100$ (\protect\showpgfcircle).}%
  \label{fig:benchmark}
  \end{figure}

@@

\begin{figure}
  \centering
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Depth},
        ylabel={Time in ms},
        xmin=1, xmax=5,
        ymin=8, ymax=2^10,
        xtick={1,2,3,4,5},
        ymode=log,
        log basis y=2,
        ymajorgrids=true,
        grid style=dashed
        ]
        \addplot[
          color=orange,
          mark=square,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 32.192292) (2, 39.246833) (3, 47.596875) (4, 53.228625) (5, 60.162625)
          };
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 75.599833) (2, 94.688208) (3, 113.647292) (4, 131.776291) (5, 148.492917) 
          };
        \addplot[
          color=orange,
          mark=o,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 101.828250) (2, 111.354459) (3, 115.116500) (4, 125.602792) (5, 130.459292) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 235.018833) (2, 319.038292) (3, 421.737083) (4, 522.937000) (5, 604.252875) 
          };
      \end{axis}
    \end{tikzpicture}
    \caption{Without precompilation}%
    \label{fig:erase-noprecomp}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Depth},
        xmin=1, xmax=5,
        ymin=8, ymax=1024,
        xtick={1,2,3,4,5},
        ymode=log,
        log basis y=2,
        %yticklabels={},
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 12.507986) (2, 17.695611) (3, 22.835264) (4, 27.568305) (5, 32.235500) 
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 7.969861) (2, 8.940027) (3, 10.796555) (4, 11.887569) (5, 13.822249) 
          };
        \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 76.545402) (2, 82.492861) (3, 88.691375) (4, 94.362653) (5, 98.254972) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 11.640499) (2, 15.205833) (3, 18.346361) (4, 21.828027) (5, 24.862680) 
          };
      \end{axis}
    \end{tikzpicture}
    \caption{With precompilation}%
    \label{fig:erase-precomp}
  \end{subfigure}
  \caption{Results of the depth benchmark for $n = 6$ with precompilation disabled (\subref{fig:erase-noprecomp}) or enabled (\subref{fig:erase-precomp}) and with $a = 0$ (\protect\showpgfsquare) or $a = 100$ (\protect\showpgfcircle).}%
  \label{fig:erase}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{subfigure}[b]{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Number of hypotheses},
        ylabel={Time in ms},
        xmin=1, xmax=32,
        ymin=4, ymax=2^16,
        %xtick={1,2,4,8,16},
        %ytick={2^3,2^5,2^7,2^9,2^11,2^13},
        xmode=log,
        ymode=log,
        log basis x=2,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=}
        ]
        \addplot[
          color=orange,
          mark=square,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 6.168695) (2, 7.647181) (4, 13.331245) (8, 91.160610) (16, 1686.694560) (32, 42247.399772) 
          };
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 7.279874) (2, 9.579929) (4, 14.167385) (8, 33.641056) (16, 152.281068) (32, 1003.538712)
          };
        \addplot[
          color=orange,
          mark=o,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 8.599714) (2, 19.510758) (4, 123.130497) (8, 1535.950129) (16, 22642.477537) (32, 371185.740641)
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 11.817681) (2, 22.297554) (4, 58.571268) (8, 204.596366) (16, 870.644077) (32, 3748.262977)
          };
      \end{axis}
    \end{tikzpicture}
    \caption{Transitivity benchmark}%
    \label{fig:trans}
  \end{subfigure}%
  \begin{subfigure}[b]{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Number of rules},
        %ylabel={Time in ms},
        xmin=1, xmax=32,
        ymin=4, ymax=2^16,
        ymode=log,xmode=log,
        log basis x=2,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 8.376025) (2, 12.775183) (4, 36.042362) (8, 179.360097) (16, 1149.268666) (32, 8300.053437) 
          };
          \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 10.400941) (2, 12.097460) (4, 15.495423) (8, 22.644318) (16, 37.950312) (32, 70.298812)
          };
          \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 13.713279) (2, 23.140410) (4, 57.941920) (8, 234.314904) (16, 1378.349248) (32, 9612.427347) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 20.117926) (2, 30.537418) (4, 51.648758) (8, 95.003862) (16, 180.553745) (32, 357.379087)
          };
      \end{axis}
    \end{tikzpicture}
    \caption{Independence benchmark}%
    \label{fig:indep}
  \end{subfigure}
  \caption{Results of the transitivity (\subref{fig:trans}) and independence (\subref{fig:indep}) benchmarks for $a = 0$ (\protect\showpgfsquare) and $a = 100$ (\protect\showpgfcircle).}%
  \label{fig:benchmark}
  \end{figure}

@@

\begin{figure}
  \centering
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Depth},
        ylabel={Time in ms},
        xmin=1, xmax=5,
        ymin=8, ymax=2^10,
        xtick={1,2,3,4,5},
        ymode=log,
        log basis y=2,
        ymajorgrids=true,
        grid style=dashed
        ]
        \addplot[
          color=orange,
          mark=square,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 29.711047) (2, 36.485449) (3, 43.350398) (4, 50.436345) (5, 57.259252) 
          };
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 74.253768) (2, 92.385454) (3, 110.028423) (4, 127.629943) (5, 144.888551) 
          };
        \addplot[
          color=orange,
          mark=o,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 98.821245) (2, 106.618691) (3, 114.094895) (4, 122.223695) (5, 129.960526) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 225.777493) (2, 318.982995) (3, 410.668802) (4, 501.413283) (5, 592.961541) 
          };
      \end{axis}
    \end{tikzpicture}
    \caption{Without precompilation}%
    \label{fig:erase-noprecomp}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Depth},
        xmin=1, xmax=5,
        ymin=8, ymax=1024,
        xtick={1,2,3,4,5},
        ymode=log,
        log basis y=2,
        %yticklabels={},
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 11.508160) (2, 16.016310) (3, 20.662793) (4, 25.250989) (5, 29.880510) 
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 6.451668) (2, 7.927170) (3, 9.389370) (4, 10.853781) (5, 12.284477)
          };
        \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 72.542545) (2, 78.261291) (3, 83.286783) (4, 88.887660) (5, 93.587293) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 9.969747) (2, 13.145151) (3, 16.236820) (4, 19.391110) (5, 22.623412)
          };
      \end{axis}
    \end{tikzpicture}
    \caption{With precompilation}%
    \label{fig:erase-precomp}
  \end{subfigure}
  \caption{Results of the depth benchmark for $n = 6$ with precompilation disabled (\subref{fig:erase-noprecomp}) or enabled (\subref{fig:erase-precomp}) and with $a = 0$ (\protect\showpgfsquare) or $a = 100$ (\protect\showpgfcircle).}%
  \label{fig:erase}
\end{figure}
